---
title: "Descriptives"
output: word_document
---

```{r setup, include=FALSE}
require(drake)
require(tidyverse)
require(knitr)
require(gtsummary)

precleaned_data <- readd(precleaned_data)
roc_data <- readd(roc_data)
change_data <- readd(change_data)
deter_data <- readd(deter_data)
moderators <- readd(moderators)
roc_data_intermediate <- readd(roc_data_intermediate)

knitr::opts_chunk$set(echo = F, warning = F, error = F, message = F)
```

An total of `r NROW(change_data)` clients from `r n_distinct(change_data$CcmhID)` center were included in analyses, although some subscales had reduced numbers due to clients not being able to go off track or deteriorate on certain subscales. Total clients and centers for each subscale are included in the results table for each model.  

# Internal consistency of CCAPS in this sample
```{r}
alpha_data <- filter(precleaned_data, Is_ValidCCAPS == 1) %>% 
  filter(UniqueClientID %in% change_data$UniqueClientID) %>% 
  arrange(UniqueClientID, Date) %>% 
  group_by(UniqueClientID) %>% 
  slice(1) %>% 
  ungroup() %>% 
  select(CCAPS_01:CCAPS_70)

alpha_data$CCAPS_18r <- abs(alpha_data$CCAPS_18-4)
alpha_data$CCAPS_39r <- abs(alpha_data$CCAPS_39-4)

alphas <- data.frame(Subscale = c("Depression", "Generalized_Anxiety", "Social_Anxiety", "Academics", "Eating", "Hostility",  "Alcohol", "DI"), Alpha = NA)
alphas[1,2] <- psychometric::alpha(dplyr::select(alpha_data, c(CCAPS_11, CCAPS_13,CCAPS_24, CCAPS_27, CCAPS_45, CCAPS_51))) #Depression34
alphas[2,2] <- psychometric::alpha(dplyr::select(alpha_data, c(CCAPS_05, CCAPS_17,CCAPS_21, CCAPS_22, CCAPS_31, CCAPS_34))) #Anxiety34
alphas[3,2] <- psychometric::alpha(dplyr::select(alpha_data, c(CCAPS_03,CCAPS_39r, CCAPS_46, CCAPS_49, CCAPS_52))) #Social Anxiety
alphas[4,2] <- psychometric::alpha(dplyr::select(alpha_data, c(CCAPS_18r, CCAPS_57, CCAPS_59, CCAPS_66))) #Academics
alphas[5,2] <- psychometric::alpha(dplyr::select(alpha_data, c(CCAPS_06, CCAPS_16, CCAPS_29))) #Eating
alphas[6,2] <- psychometric::alpha(dplyr::select(alpha_data, c(CCAPS_36, CCAPS_40, CCAPS_48, CCAPS_58, CCAPS_64, CCAPS_68))) #Hostility
alphas[7,2] <- psychometric::alpha(dplyr::select(alpha_data, c(CCAPS_30, CCAPS_33,CCAPS_54, CCAPS_63))) #Alcohol
alphas[8,2] <- psychometric::alpha(dplyr::select(alpha_data, c(CCAPS_05, CCAPS_11, CCAPS_13, CCAPS_17, CCAPS_21, CCAPS_22, CCAPS_24,CCAPS_27, CCAPS_31, CCAPS_34, CCAPS_40, CCAPS_45,CCAPS_46, CCAPS_48, CCAPS_51, CCAPS_52, CCAPS_57, CCAPS_58, CCAPS_59, CCAPS_66))) # DI
alphas[,2] <- round(alphas[,2], 2)
alphas <- alphas %>%
  column_to_rownames("Subscale") %>%
  t() %>%
  as_tibble() %>%
  mutate(alpha = "Overall alpha", .before = 1)
```
Internal consistencies for CCAPS subscales from data included in the present study were in line with established psychometrics for this scale, with alphas ranging from `r min(alphas$Alpha)` on `r alphas$Subscale[which.min(alphas$Alpha)]` and `r max(alpha$Alpha)` on `r alphas$Subscale[which.max(alphas$Alpha)]`. 

# Flow chart of clients lost at each step
```{r}
# Starting N of clients and centers contributing data for all 4 years
data_flow_chart <- data.frame(Step = "Starting N- Centers contributing all 4 years", Clients = n_distinct(precleaned_data$UniqueClientID), Centers = n_distinct(precleaned_data$CcmhID))

# 1+ attended individual session
data <- CCMHr::create_courses(precleaned_data, firstOnly = T)
data <- mutate(data, Is_appointment = ifelse(!is.na(AppointID), 1, 0))
appts <- filter(data, Is_appointment == 1)
ccaps <- filter(data, Is_ValidCCAPS == 1)
appts <- filter(appts, ClientAttendance == "Attended") %>%
  filter(AppointmentCategory == 2|AppointmentCategory == 3|AppointmentCategory == 4)
data_flow_chart2 <- rbind(data_flow_chart, data.frame(Step = "1+ attended individual appt", Clients = n_distinct(appts$UniqueClientID), Centers = n_distinct(appts$CcmhID)))

# 3+ attended individual appts
appts$duplicate <- duplicated(appts[c("UniqueClientID", "Date")])
appts <- filter(appts, duplicate == FALSE) %>%
  select(-duplicate)
appts <- group_by(appts, UniqueClientID) %>%
  filter(n() >= 3) %>%
  mutate(appt_seq = row_number(), appt_N = n()) %>%
  select(UniqueClientID, CcmhID, Date, appt_seq, appt_N)
data_flow_chart3 <- rbind(data_flow_chart2, data.frame(Step = "3+ attended individual appt", Clients = n_distinct(appts$UniqueClientID), Centers = n_distinct(appts$CcmhID)))

# 3+ individual appts with CCAPS
ccaps$duplicate <- duplicated(ccaps[c("UniqueClientID", "Date")])
ccaps <- filter(ccaps, duplicate == FALSE) %>%
  select(-duplicate)
ccaps <- group_by(ccaps, UniqueClientID) %>%
  filter(n() >= 3) %>%
  mutate(CCAPS_seq = row_number(), CCAPS_N = n()) %>%
  select(UniqueClientID, CcmhID, Date, CCAPS_seq, CCAPS_N, Depression34:DI)
combined <- merge(x = appts, y = ccaps, by = c("UniqueClientID", "Date", "CcmhID"), all.x = TRUE) %>%
  group_by(UniqueClientID) %>%
  mutate(CCAPS_N = max(CCAPS_N, na.rm = T), appt_N = max(appt_N, na.rm = T)) %>%
  mutate(matched_CCAPS_N = sum(!is.na(DI))) %>%
  filter(matched_CCAPS_N >= 3)
combined20 <- filter(combined, appt_seq <= 20) %>%
  group_by(UniqueClientID) %>%
  mutate(matched_CCAPS_N = sum(!is.na(DI))) %>%
  filter(matched_CCAPS_N >= 3) %>%
  ungroup()
data_flow_chart4 <- rbind(data_flow_chart3, data.frame(Step = "3+ individual appts with CCAPS", Clients = n_distinct(combined20$UniqueClientID), Centers = n_distinct(combined20$CcmhID)))

# CCAPS at first appt
combined_first <- group_by(combined20, UniqueClientID) %>%
  filter(!is.na(first(Depression34))) %>%
  mutate_at(vars(Depression34:DI), list(first = first)) %>%
  ungroup()
data_flow_chart5 <- rbind(data_flow_chart4, data.frame(Step = "CCAPS at first appointment", Clients = n_distinct(combined_first$UniqueClientID), Centers = n_distinct(combined_first$CcmhID)))
  
# Missing hx moderator
combined_hx <- left_join(combined_first, moderators) %>% 
  filter(!is.na(hospitalization))
data_flow_chart6 <- rbind(data_flow_chart5, data.frame(Step = "Complete data on moderators", Clients = n_distinct(combined_hx$UniqueClientID), Centers = n_distinct(combined_hx$CcmhID)))

rename(data_flow_chart6, `Data cleaning step` = Step, `Client N` = Clients, `Center N` = Centers) %>% 
  kable()
```

# Number of sessions & distribution
```{r}
sessions <- group_by(roc_data, UniqueClientID) %>% 
  slice(1) %>% 
  ungroup() %>% 
  select(appt_N)
```

After removing sessions above 20, clients' total number of sessions ranged from 3 to 20 with a mean of `r round(mean(sessions$appt_N),2)`, a SD of `r round(sd(sessions$appt_N),2)`,  a median of `r median(sessions$appt_N)`, and a mode of `r CCMHr::get_mode(sessions$appt_N)`. 

# Average change
```{r}

```

# Proportion of clients who went off track, overall and before and after feedback
```{r}
alerts <- group_by(roc_data, UniqueClientID, feedback) %>% 
  summarize(across(contains("alert"), max, na.rm = T)) %>% 
  ungroup() %>% 
  mutate(across(contains("alert"), function(x) ifelse(!is.finite(x), NA, x)))

alerts_condition <- group_by(alerts, feedback) %>% 
  summarize(across(contains("alert"), function(x) scales::percent(mean(x, na.rm = T), accuracy = .01)))

alerts_overall <- summarize(alerts, across(contains("alert"), function(x) mean(x, na.rm = T))) %>% 
  t() %>% 
  as.data.frame() %>% 
  rename(alert_percent = V1) %>% 
  rownames_to_column("subscale") %>% 
  filter(subscale != "alert_any") %>% 
  mutate(subscale = str_remove(subscale, "_alert"),
         subscale = str_remove(subscale, "34")) 
  
```
Across both feedback conditions, `r scales::percent(mean(alerts$alert_any), accuracy = .01)` of clients went off track on at least one subscale at some point during treatment, and this was identical across no feedback and feedback conditions. The percentage of clients going off track on each subscale ranged from `r scales::percent(min(alerts_overall$alert_percent), .01)` on the `r alerts_overall$subscale[which.min(alerts_overall$alert_percent)]` to `r scales::percent(max(alerts_overall$alert_percent), .01)` on `r alerts_overall$subscale[which.max(alerts_overall$alert_percent)]`. The proportion of clients going off track on each subscale also did not differ between conditions. 

# When in tx alerts occur
Proportions of sessions with alerts and number of alerts 
```{r}
alert_data <- session_alerts(roc_data_intermediate)

alert_data <- group_by(alert_data, appt_seq, subscale) %>% 
  summarize(N = n(), alert_n = sum(alert), alert_prop = mean(alert))
```

# Table of moderators by feedback status
```{r}
mods_summary <- roc_data_intermediate %>% 
  group_by(UniqueClientID) %>% 
  slice(1) %>% 
  ungroup() %>% 
  mutate(feedback = ifelse(feedback == 1, "Feedback", "No feedback"),
         hospitalization = ifelse(hospitalization == 1, "Yes", "No")) %>% 
  select(feedback, Depression34:DI, hospitalization, appt_N) # TODO: add ccaps_freq once it's double checked
  

mods_table <- tbl_summary(
  mods_summary,
  by = feedback) %>%
  add_n() %>% # add column with total number of non-missing observations
  add_p() %>% # test if there's difference between groups
  bold_labels() 

finalfit::summary_factorlist(mods_summary, "feedback", 
                             c("Depression34", "Anxiety34", "Social_Anxiety34", "Academics34", "Eating34", "Hostility34", "Alcohol34", "DI", "hospitalization", "appt_N")) 
  knitr::kable(align=c("l", "l", "r", "r", "r"))
```

